%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Deedy CV/Resume
% The original template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume} 

\begin{document}
%
%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------
%
\lastupdated % Print the Last Updated text at the top right
 
\begin{minipage}[t]{0.68\textwidth}

\blockspace
\namesection{Anton}{Ugarov}{Highly qualified Software Engineer with 6+ years of expertise in C++ development. Specializing in high-performance backend systems and real-time data processing. }

\end{minipage}
\hfill
\columnspace
%
%----------------------------------------------------------------------------------------
%	CONTACTS & LINKS
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.27\textwidth}

\blockspace
\colorbox{shade}{
\begin{supertabular}{@{\hspace{3pt}} p{0.05\linewidth} p{0.775\linewidth}} 
    \raisebox{-1pt}{\faHome} & Zürich, Switzerland \\
    \raisebox{-1pt}{\small\faEnvelope} & \href{mailto:augarov.swe@gmail.com}{\bf augarov.swe@gmail.com} \\
    \raisebox{-1pt}{\faLinkedin} & \href{https://www.linkedin.com/in/augarov}{\bf linkedin.com/in/augarov} \\
    \raisebox{-1pt}{\faTelegramPlane} & \href{https://t.me/augarov_swe}{\bf t.me/augarov\_swe} \\
    \raisebox{-1pt}{\faGithub} & \href{https://github.com/Deligor6321}{\bf github.com/Deligor6321} \\
\end{supertabular}
}

\end{minipage}

\blockspace

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.25\textwidth}

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\textbf{Expert:}
\begin{skillitemize}
    \skillitem C++ 
    \skillitem STL
    \skillitem Multithreading
    \skillitem Performance
\end{skillitemize}

\textbf{Intermediate:}
\begin{skillitemize}
    \skillitem Boost
    \skillitem Python
    \skillitem TCP/IP
    \skillitem HTTP
    \skillitem Protobuf
    \skillitem PostgreSQL
    \skillitem CMake
    \skillitem Bash
    \skillitem Git
    \skillitem Linux
    \skillitem Docker/Compose
\end{skillitemize}

\textbf{Basic:}
\begin{skillitemize}
    \skillitem Go
    \skillitem OpenCV
    \skillitem MetalKit
\end{skillitemize}

\sectionspace 

\textbf{Soft Skills:}
\begin{skillitemize}
    \skillitem Responsibility
    \skillitem Effective communication
    \skillitem Problem-solving
    \skillitem Team collaboration
\end{skillitemize}

\sectionspace

%------------------------------------------------
% Languages
%------------------------------------------------

\section{Languages}
\textbf{English} / C1 \\
\textbf{Russian} / native \\
\textbf{Deutsch} / A1 (learning)

\sectionspace

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\runsubsection{State Electrotechnical University "LETI"} \\
\descript{BS in Computer Science}
\location{2015 - 2019 | St. Petersburg}
Computer Systems Engineering and Informatics \\
Specialization: Computer Aided Design Systems \\
\textbf{Cum. GPA}: \textit{4.57 / 5.0} \\
\textbf{Major GPA}: \textit{4.60 / 5.0}

\sectionspace

%----------------------------------------------------------------------------------------

\end{minipage}
\hfill
\columnspace
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.70\textwidth}

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Self Employed}
\descript{| Senior Software Engineer}
\location{Apr 2024 - PRESENT | Zürich, Switzerland}

Collaborating with a dynamic startup in a fast-paced environment.
Developing a \textbf{high-load C++20 backend} for real-time telemetry and event aggregation, efficiently processing and manipulating \textbf{large-scale data streams} at 200Mbps per core.
\begin{descritemize}
    \descritem Leveraged C++ \textbf{coroutines} with the Seastar framework for efficient concurrency.
    \descritem Utilized the Ragel state machine compiler \textbf{reducing the parsing time} of standard event formats (SyslogBSD, CEF) by 70\%.
    \descritem Led availability enhancements, \textbf{eliminating downtime} during service upgrades
    \descritem \textbf{Built a sandbox service} for debugging data aggregation with step-by-step insights.
    \descritem \textbf{Reverse-engineered} and implemented a proprietary 3rd-party binary protocol.
\end{descritemize}
\textbf{Stack}: \textit{C++20 / Seastar / Boost / Ragel / Docker / AWS / Python / Jinja / Go}

\sectionspace

%------------------------------------------------

\runsubsection{WANNA}
\descript{| Senior Software Engineer}
\location{Jun 2022 - Apr 2024 | Limassol, Cyprus}

Developed a \textbf{lightweight cross-platform C++20 library} enabling virtual try-on experiences on \textbf{mobile devices}.
\begin{descritemize}
    \descritem \textbf{Designed a universal C API} for seamless interaction with native platform frontends, encapsulated by Objective-C glue code. 
    \descritem Built a \textbf{generic 3D viewer} with smooth animations and high performance at 60FPS, establishing it as a core offering for the company.
    \descritem Upgraded the codebase to a \textbf{new render engine} unlocking realistic reflections.
\end{descritemize}
\textbf{Stack}: \textit{C++20 / Objective-C / OpenCV / Metal / CoreML / CMake / Conan / GoogleTest}

\sectionspace

%------------------------------------------------

\runsubsection{Yandex}
\descript{| Software Engineer}
\location{Mar 2020 - May 2022 | St. Petersburg, Russia}

Developed a \textbf{high-load C++17 backend} for Yandex.Messenger, serving 20kRPS, with a focus on efficient and secure asynchronous code to ensure \textbf{system resilience}.
\begin{descritemize}
    \descritem Contributed to \textbf{core service components}: Json/Protobuf APIs, message processing pipeline, and data storage (PostgreSQL/YDB).
    \descritem Boosted system scalability by implementing  \textbf{sharding and load balancing}, resolving bottlenecks in the support-automation service.
    \descritem Optimized in-memory cache storage, \textbf{reducing RAM consumption} by 10\%.
    \descritem Integrated probabilistic data structures to count unique message views in large channels, \textbf{reducing the space complexity} significantly.
    \descritem Gained Python experience while \textbf{developing the auxiliary services}.
\end{descritemize}
\textbf{Stack}: \textit{C++17 / Python / Protobuf / PostgreSQL / YDB}

\sectionspace

%------------------------------------------------

\runsubsection{Tensor}
\descript{| Software Engineer}
\location{Jun 2018 - Feb 2020 | St. Petersburg, Russia}

Developed a \textbf{cross-platform C++14 / Boost library} for the business logic of an \textbf{Android/iOS} courier app.
\begin{descritemize}
    \descritem \textbf{Redesigned architecture}, cutting time-to-market for new features by 30\%.
    \descritem Developed a middle-end layer to \textbf{integrate the backend with platform-native frontends} using JsonRPC and Djinni-generated bridges.
    \descritem Built a generic \textbf{component for automatic data caching} to a local SQLite DB, ensuring reliable offline support. 
\end{descritemize}
\textbf{Stack}: \textit{C++14 / Boost / JNI / Djinni / SQLite / Conan / CMake / Boost.Test}

\sectionspace

%------------------------------------------------

\runsubsection{Confident}
\descript{| Embedded System Developer, Part-time}
\location{Mar 2018 - Jun 2018 | St. Petersburg, Russia}
\textbf{Stack}: \textit{Linux / OpenWRT / Bash / make /  GitLab CI}
\sectionspace

%------------------------------------------------

\runsubsection{Clicknet}
\descript{| Embedded System Developer, Part-time}
\location{Jul 2017 - Mar 2018 | St. Petersburg, Russia}
\textbf{Stack}: \textit{Linux / AGL / Chromium / Bash / CMake / ninja}

\end{minipage}

\end{document}